Combinatorial Proofs and Decomposition Theorems for First-order Logic

### 2021-01-14 main.tex
some more defs

\todo{examle here}

@@

>>>>

\todo{example here}

@@

If a derivation $\Deri$ contains instances of the rules $\mfaD$ and
$\mexD$ we can no longer naively define the rectification
$\rectif\Deri$ as in the previous section for $\FOMLS$, as these two
rules cannot be applied if premise and conclusion are rectified. For
this reason we define here rectified versions $\rectif\mfaD$ and
$\rectif\mexD$.
